Logsums

### 2020-01-29 03_accessibility.Rmd
Rebuild website

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
library(lubridate)
library(VGAM)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spdep)
library(spatialreg)
library(leaflet)
library(lubridate)
library(VGAM)
```
